Developing a preprint culture in biology

### 2013-02-26 ms.tex
Softening on the Conclusions intended to make the paper more generally appealing

Developing a preprint culture in biology will not solve all of the problems with
the current publication process. However, it might significantly reduce the
negative consequences. The role of peer-review is to judge the scientific
quality of a study. It is the first barrier against fraudulent and poor quality
science that could impede scientific progress. In practice, the peer-review
system is not only used to evaluate scientific quality but also to judge
pertinence. In contrast, preprints are not filtered based on either quality or
pertinence. Widespread adoption of preprint servers has the potential to shift
the distribution strategy: journals would remain important for validating
publications, but the relevance of a study should only be judged by many more
readers than the typical two to four anonymous reviewers. With a shift in the
diffusion strategy, the role of traditional journals and their editors would be
to showcase scientific discoveries for specialized readership.

Making publication easier can lead to the proliferation of studies of uneven 
quality. A trade-off between the intensity of the peer-review filtering and 
the benefits to science has been hypothesized \cite{Aarssen2012}.  With 
increasingly stringent peer review, the quality of published papers can 
improve at the cost of an increased load on authors and 
reviewers, and greater delays for publication.  By
bypassing this model preprints 
speed up the dissemination of scientific discoveries and put on reader's 
shoulders the responsibility to judge originality and pertinence.

>>>>

Developing a preprint culture in biology will not solve all of the problems with
the current publication process. However, it might significantly reduce the
negative consequences. The role of peer-review is to judge the scientific
quality of a study. It is the first barrier against fraudulent and poor quality
science that could impede scientific progress. In practice, the peer-review
system is not only used to evaluate scientific quality but also to judge
pertinence. In contrast, preprints are not filtered based on either quality or
pertinence. Widespread adoption of preprint servers has the potential to shift
the distribution strategy making scientific results immediately available to the
community, while allowing traditional journals to validate the results and
showcase scientific discoveries for their readership.

Making publication easier can lead to the proliferation of studies of uneven
quality. A trade-off between the intensity of the peer-review filtering and the
benefits to science has been hypothesized \cite{Aarssen2012}.  With increasingly
stringent peer review, the quality and perceived importance of published papers
may be improved, but at the cost of an increased load on authors and reviewers,
and greater delays for publication.  By developing a preprint culture in biology
we can speed up the dissemination of scientific discoveries and potentially
improve the quality of initial submissions to journals through pre-publication
peer-review.
